---
title: "Hospitalizations - EPI1 Scenarios"
author: "Pragati Prasad"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mean, Cumulative with 95% CI, and Averted per 100K  {.tabset}


### Scenario HP01

Base Scenario: R0 1.4 and “2009-like” severity

```{r HP01, warning=FALSE, message = FALSE}

library(ggsci)
library(reshape)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(egg)
library(plyr)
library(tidyr)
library(knitr)
library(kableExtra)

path <- "../model-forecasts/"

team.folder <- c("Columbia/COL/EPI1/", "Northeastern/EPI1/", "UTAustin/", "UVirginia/", "Imperial/", "Columbia/COL2/EPI1/")
team.abbrev <- c("COL", "NEU", "UTA", "UVA", "IMP", "COL2")
file.types <-c("SymIllness", "Hosp", "Deaths", "AntiviralTX")
scn = "HP01_"
read_overall_mean <- function(scn){
  
  cols <- c("sm.mean", "sm.perc2p5", "sm.perc97p5")

  s <- read.csv(paste0(path,team.folder[1],scn,file.types[2],"_",team.abbrev[1],".csv"))
  hosp <- data.frame(c(s[which(s$Agegroup == "Overall" &
                                       s$Bin %in% cols),],
                             `team` = team.abbrev[1]))
  
  for(i in 2:6){
    
    if(i == 4){
      scn = gsub("HP", "HP_", scn)
    }
    if(i == 5){
      scn = gsub("_", "", scn)
    }
    if(i == 6){
      scn = paste0(scn, "_")
    }
    f = paste0(path,team.folder[i],scn,file.types[2],"_",team.abbrev[i],".csv")
    if(i == 5){
      f =  paste0(path,team.folder[i],scn,file.types[2],team.abbrev[i],".csv")
    }
    if(file.exists(f)){
      s <- read.csv(f)
      if(ncol(s) > 58){
        s <- s[-1]
      }
      hosp <- rbind.fill(hosp, 
                               data.frame(c(s[which(s$Agegroup == "Overall" & 
                                                      s$Bin %in% cols),],`team` = team.abbrev[i])))
    }
    
  }
  weeks <- paste0("Week",1:52)
  hosp$Cml[which(is.na(hosp$Cml))] <- hosp$cml[which(is.na(hosp$Cml))]
  cml <<- hosp[c("Cml", "team", "Bin")]
  
  long <- gather(hosp, week, illnesses, weeks, factor_key=TRUE)
  long$week <- as.integer(gsub("Week", "", long$week))
  
  cols <- c("Bin", "team", "week", "illnesses")
  long <- long[cols]
  long_wide <- spread(long, Bin, illnesses)
  
  return(long_wide)
}

long_HP01 <- read_overall_mean(scn = "HP01_")

ggplot(data = long_HP01, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

rownames(table) <- NULL

knitr::kable(table[5:7], digits = 2, caption = "HP01, No Intervention", align=rep('c', 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


table1 <- table


team.folder <- c("Columbia/COL/EPI1/", "Northeastern/EPI1/", "UTAustin/", "UVirginia/", "Imperial/", "Columbia/COL2/EPI1/")
team.abbrev <- c("COL", "NEU", "UTA", "UVA", "IMP", "COL2")
file.types <-c("SymIllness", "Hosp", "Deaths", "AntiviralTX")
scn = "HP01_"

read_ages <- function(scn){
  
  cols <- c("sm.mean")

  s <- read.csv(paste0(path,team.folder[1],scn,file.types[2],"_",team.abbrev[1],".csv"))
  hosp <- data.frame(c(s[which(s$Agegroup != "Overall" &
                                       s$Bin %in% cols),],
                             `team` = team.abbrev[1]))
  
  for(i in 2:6){
    
    if(i == 4){
      scn = gsub("HP", "HP_", scn)
    }
    if(i == 5){
      scn = gsub("_", "", scn)
    }
    if(i == 6){
      scn = paste0(scn, "_")
    }
    f = paste0(path,team.folder[i],scn,file.types[2],"_",team.abbrev[i],".csv")
    if(i == 5){
      f =  paste0(path,team.folder[i],scn,file.types[2],team.abbrev[i],".csv")
    }
    if(file.exists(f)){
      s <- read.csv(f)
      if(ncol(s) > 58){
        s <- s[-1]
      }
      hosp <- rbind.fill(hosp, 
                               data.frame(c(s[which(s$Agegroup != "Overall" & 
                                                      s$Bin %in% cols),],`team` = team.abbrev[i])))
    }
    
  }
  weeks <- paste0("Week",1:52)
  hosp$Cml[which(is.na(hosp$Cml))] <- hosp$cml[which(is.na(hosp$Cml))]
  cml <- hosp[c("Cml", "team", "Bin", "Agegroup")]
  cml$Agegroup <- sub("yr", "years", cml$Agegroup)
  cml$Agegroup <- factor(x = cml$Agegroup, levels = c("0-4 years", "5-17 years", "18-49 years", "50-64 years", "65+ years"))

  return(cml)
}

ages_1 <- read_ages(scn = "HP01_")
ggplot(ages_1, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()
```

### HP02

VX1

“Early”: Vaccine available 100 days after September 1

```{r HP02, warning=FALSE, message = FALSE}

scenario <- "HP02_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP02: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`)
averted_age <- data.frame(scenario = scenario,
                         team = ages$team,
                         agegroup = ages$Agegroup,
                         reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml )
```


### HP03

VX2

“Normal”: Vaccine available 150 days after September 1

```{r HP03, warning=FALSE, message = FALSE}

scenario <- "HP03_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP03: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```


### HP04

SC1

Weekly Symptomatic Prevalence > 1% trigger, early (VX1) vaccine availability reopening

```{r HP04, warning=FALSE, message = FALSE}

scenario <- "HP04_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team, color = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), 
              alpha = 0.3,
              linetype=0,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP04: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```


### HP05

SC2

Close on October 28, early (VX1) vaccine availability reopening

```{r HP05, warning=FALSE, message = FALSE}

scenario <- "HP05_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP05: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```


### HP06

SC3

Weekly Symptomatic Prevalence > 1% trigger, normal (VX2) vaccine availability reopening

```{r HP06, warning=FALSE, message = FALSE}

scenario <- "HP06_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP06: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```



### HP07

SC4

Close on October 28, normal (VX2) vaccine availability reopening

```{r HP07, warning=FALSE, message = FALSE}

scenario <- "HP07_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP07: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```


### HP08

AV

Antivirals

```{r HP08, warning=FALSE, message = FALSE}

scenario <- "HP08_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP08: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```


### HP09

VX1 & SC1 & AV

* “Early”: Vaccine available 100 days after September 1 
* Weekly Symptomatic Prevalence > 1% trigger, early (VX1) vaccine availability reopening  
* Antivirals

```{r HP09, warning=FALSE, message = FALSE}

scenario <- "HP09_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP09: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```

### HP10

VX1 & SC2 & AV

* “Early”: Vaccine available 100 days after September 1 
* Close on October 28, early (VX1) vaccine availability reopening  
* Antivirals

```{r HP10, warning=FALSE, message = FALSE}

scenario <- "HP10_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP10: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```

### HP11

VX2 & SC3 & AV

* “Normal”: Vaccine available 150 days after September 1 
* Weekly Symptomatic Prevalence > 1% trigger, normal (VX2) vaccine availability reopening  
* Antivirals

```{r HP11, warning=FALSE, message = FALSE}

scenario <- "HP11_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP11: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
```

### HP12

VX2 & SC4 & AV

* “Normal”: Vaccine available 150 days after September 1 
* Close on October 28, normal (VX2) vaccine availability reopening  
* Antivirals

```{r HP12, warning=FALSE, message = FALSE}

scenario <- "HP12_"

long <- read_overall_mean(scn = scenario)

ggplot(data = long, aes(x = week, y = sm.mean, group = team)) +
  geom_line(aes(color = team), lwd = 1.0) +
  geom_ribbon(aes(ymin = sm.perc2p5, ymax = sm.perc97p5, fill = team), alpha = 0.3,
              show.legend = FALSE)+
  ylab("Hospitalizations per 100,000") +
  scale_color_nejm() +
  scale_fill_nejm()


table <- cml[which(cml$Bin == "sm.mean"),]
table <- table[,-3]

table$lower <-  cml$Cml[which(cml$Bin == "sm.perc2p5")]
table$upper <-  cml$Cml[which(cml$Bin == "sm.perc97p5")]
table$Team <- table$team
table$`Cum. Hospitalizations per 100K` <- table$Cml
table$`95% CI` <- paste0("(", round(table$lower, 2), ", ", round(table$upper, 2), ")")

table$`Averted Hospitalizations per 100K (HP01)` <- ifelse(table$Team %in% table1$Team, table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`, NA)
table$`% Reduction in Burden (HP01)` <- ifelse(table$Team %in% table1$Team, 100 * (table1$`Cum. Hospitalizations per 100K` - table$`Cum. Hospitalizations per 100K`) / table1$`Cum. Hospitalizations per 100K`, NA)

rownames(table) <- NULL

knitr::kable(table[5:9], digits = 2, caption = "HP12: Compared to HP01", align=rep('c', 4)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#Bar chart for ages
ages <- read_ages(scn = scenario)
ggplot(ages, aes(fill=Agegroup, y=Cml, x=team)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Percent")+
  scale_fill_d3()

averted <- rbind(averted, data.frame(scenario = rep(scenario, nrow(table)),
                                     team = table$Team,
                                     reduction = table$`% Reduction in Burden (HP01)`))
averted_age <- rbind(averted_age, data.frame(scenario = scenario,
                                             team = ages$team,
                                             agegroup = ages$Agegroup,
                                             reduction = 100*(ages_1$Cml - ages$Cml) / ages_1$Cml ))
write.csv(averted, "Hospitalizations_EPI1.csv")
write.csv(averted_age, "Hospitalizations_age_EPI1.csv")
```